### 2020-05-31 README.Rmd
update 2020-05-31 20:24:18
update 2020-05-31 20:28:51

```{r, echo = FALSE}
knitr::include_graphics("paper/workflow_graph/workflow.png")
```

@@

The WORCS paper and `worcs` package are open to contributions from collaborators with valuable expertise, to improve both the workflow and the package. Relevant contributions warrant coauthorship to the paper or package. Please contact the lead author at [c.j.vanlissa@uu.nl](mailto:c.j.vanlissa@uu.nl), or:

>>>>

```{r, echo = FALSE}
knitr::include_graphics("https://github.com/cjvanlissa/worcs/raw/master/paper/workflow_graph/workflow.png")
```

@@

The `worcs` package is open to contributions from collaborators with valuable expertise, to improve both the workflow and the software. Relevant contributions warrant coauthorship to the package. Please contact the lead author at [c.j.vanlissa@uu.nl](mailto:c.j.vanlissa@uu.nl), or:
